\large{Vipassana for Hackers} \\ \Huge{The Proposal} \\ \large\textit{Version 0.1}

### 2019-12-01 the-proposal/the-proposal.tex
proposal: problem statement-phenomenology

>>>>

Because Vipassana does not permit any form of imagination, any attempt to analyze it
through philosophical phenomenology becomes a hindrance to actually practicing
Vipassana. \cite{patrik1994phenomenological} I have previously discussed this paradox
in \textit{Vipassana for Hackers, Paper One: Curious Mechanics} \cite{deobald2017curious}
